\documentclass[12pt, a4paper, twocolumn]{article}
% Packages
\usepackage{xurl}
\usepackage{abstract}
\usepackage{lipsum}
\usepackage{sectsty}
\usepackage{newclude}
\usepackage{tocloft}
\usepackage{graphicx}
\usepackage{float}
\usepackage{titlesec}
\usepackage{dblfloatfix}
\usepackage{enumitem}
\usepackage{silence}
\usepackage{multicol}
\usepackage{tabularx}
\usepackage[hypcap=false, justification=centering]{caption}
\usepackage[none]{hyphenat}
\usepackage[numbers, super, comma, sort&compress]{natbib}
\usepackage[a4paper, margin=1.5cm]{geometry}
\usepackage{hyperref}
% Font
\usepackage{stix2}

% Configuration - https://tex.stackexchange.com/questions/110406/two-column-article-templates
\renewcommand{\abstractnamefont}{\normalfont\bfseries}
\renewcommand{\abstracttextfont}{\normalfont\small\itshape}
\renewcommand{\cftdotsep}{1}
\renewcommand{\bibsection}{}
\renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}
\hypersetup{colorlinks=false, urlcolor=blue, linkcolor=blue, citecolor=blue}
\sectionfont{\fontsize{16}{15}\selectfont}
\subsectionfont{\large}
\subsubsectionfont{\fontsize{12}{15}\selectfont}
\hbadness=99999 
% List spacing - https://tex.stackexchange.com/questions/10684/vertical-space-in-lists
\newenvironment{mylist}
{ \vspace{-0.5em}
   \begin{itemize}[leftmargin=1em]
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
}{ 
  \end{itemize}
} 

% Adjusting space
\titlespacing*{\section}{0pt}{1em}{0.4em}
\titlespacing*{\subsection}{0pt}{1em}{0.5em}
\titlespacing*{\subsubsection}{0pt}{1em}{0.5em}

% Adjusting contents space
\setlength{\cftbeforesecskip}{1pt}
\setlength{\cftbeforesubsecskip}{1pt}
\setlength{\cftaftertoctitleskip}{4pt}

% Abstract
\newcommand{\abstractText}{
  To address the issue of electronic waste and cluttered workspaces in the Level 1 Labs, this project aims to develop an automated system for identifying and sorting electronic components.
  Utilising computer vision techniques, the system will classify components like resistors, capacitors, ICs, and MOSFETs, and sort them into designated bins.
  The project will be executed in three stages: initial development of a computer vision system for component identification, integration of a semi-automated sorting mechanism, and potentially, full automation of the sorting process or additional features like IC testing.
  Supervised by Dr. Edward Stott, this project aims to practically solve the problems faced by the Level 1 Labs. \\
  \indent I affirm that I have provided explicit references for all the material in my Interim Report that is not authored by me but is represented as my work.
  I have used GPTv4, as an aid in the preparation of my report. It was used for LaTeX formatting and spellchecking, however all technical content is original.
}

% Title
\title{Interim Report}
\vspace{-2em}
\author{Shaheen Amin, 01866464 \and Dr. Edward Stott, Supervisor}
\vspace{-1em}
\date{October 2023}
\vspace{-1em}
\begin{document}
\twocolumn[
  \begin{@twocolumnfalse}
    \maketitle
    \vspace{-3.25em}
    \renewcommand*\abstractname{Abstract \& Plagiarism Declaration}
    \begin{abstract}
        \vspace{-1em}
        \abstractText
    \end{abstract}
  \end{@twocolumnfalse}
]

% Contents page
\vspace{1em}
\tableofcontents
\newpage
% Sections and Figures
\include*{Project Specification}
% Background
\include*{Background}
% Implementation
\include*{Implementation}
% Project Plan
\include*{Project Plan}
% Evaluation Plan
\include*{Evaluation Plan}
% Safety Plan
\include*{Safety Plan}
% References
\section{References}
\bibliographystyle{plainnat}
\bibliography{References}

% Appendices
\include*{Appendix}

\end{document}