\subsubsection{Electronics (and Safety)}
As my project is a physical system, there are several electronic components that are required to make the system work.

\noindent
\textbf{Power Supply} \\
As mentioned in Sections \ref*{sec:hardware} and \ref*{sec:mechanics}, the system is powered by a 24V, 6.25A, 150W power supply, and must
be stepped down to 5V for the Pi and 12V for the LED strip. This is achieved using a XL4015 Step Down Converter\cite{xl4015}, a variable
step down converter that can output up to 75W.
The high power rating of the step down converter allows for a large overhead, which is useful for future stages of the project where 
additional components may be added to the system.

For powering the system, I have chosen a standard IEC C14 power connector and a RS Pro Snap-In Fused Rocker Switch\cite{rsproc14switch}.
As the power supply is a 6.25A power supply, I have chosen a 6A fuse for the switch, which is the closest fuse rating to the power supply's
current rating. This ensures that the fuse will blow before the power supply is damaged, should there be a short circuit in the system.

For wiring the power supply and connecting the step down converters, I have chosen 18AWG wire, which is rated for 17A\cite{18awgwire}, 
more than enough for the system's power consumption. The wire is securely crimped to the power supply using a crimping tool.

\noindent
\textbf{Raspberry Pi 4} \\
To power the Raspberry Pi, I have chosen a standard USB-A to USB-C cable and connected it to a female USB-A breakout board connected to the
5V step down converter. This allows for easy removal of the Pi should I need to make changes to the system, and prevents the unnecessary
cutting of cables.

As the Pi is mounted to the LCD display, a USB-A to Micro USB cable is used to connect the Pi to the display, which is then connected to the
Pi's HDMI port, using a supplied HDMI adapter board.

\noindent
\textbf{LED Lighting} \\
As mentioned in Section \ref*{sec:hardware}, initially, a 12V LED Light Ring was used and was changed to be a WS2812B 5V LED strip, for issues described 
later. As shown in Figure \ref*{fig:wiringschematic}, the LED Ring was connected to a 12V supply (achieved using the 12V step down converter) and
parallel to a 100$\mu$F capacitor, which is used to smooth out the voltage spikes.

The LED Ring was then connected to an N-channel MOSFET IRLZ44N\cite{irlz44n}, which is controlled by a PWM-enabled GPIO pin on the Pi.
This GPIO pin is connected to a 1k$\Omega$ resistor, which prevents potential overcurrent from damaging the Pi. The MOSFET is then connected to ground, completing the circuit.

The IRFZ44N is a logic level MOSFET, meaning it can be fully turned on with a 3.3V gate voltage, which is the voltage of the Pi's GPIO pins, and the high
switching speed (up to 1mHz) of the MOSFET allows for the LED Ring to be PWM controlled, allowing for the brightness of the LED Ring to be controlled.